### 2024-10-03 MetadataS1/tables/table_species_name_strategy.tex
Revision of the entire document and minor changes

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Tue Oct  1 09:17:32 2024
\begin{table}[ht]
\centering
\caption{Species composition of the vertebrate community of Bylot Island with the corresponding migratory status (i.e., resident, partial migrant or migrant).} 
\label{table:table_species_name_strategy}
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabularx}{0.95\textwidth}{llll}
  \hline
Functional group & Scientific name & English name & Migratory status \\ 
  \hline
Ducks and loons  & Gavia pacifica & Pacific loon & migrant \\ 
  Ducks and loons  & Gavia stellata & Red-throated loon & migrant \\ 
  Ducks and loons  & Somateria spectabilis & King eider & migrant \\ 
  Ducks and loons  & Clangula hyemalis & Long-tailed duck & migrant \\ 
  Geese and swans  & Branta hutchinsii & Cackling goose & migrant \\ 
  Geese and swans  & Anser caerulescens & Snow goose & migrant \\ 
  Geese and swans  & Cygnus columbianus & Tundra swan & migrant \\ 
  Raptors  & Buteo lagopus & Rough-legged hawk & migrant \\ 
  Raptors  & Falco peregrinus & Peregrine falcon & migrant \\ 
  Raptors  & Bubo scandiacus & Snowy owl & migrant \\ 
  Ptarmigans  & Lagopus muta & Rock ptarmigan & resident \\ 
  Cranes  & Antigone canadensis & Sandhill crane & migrant \\ 
  Shorebirds  & Pluvialis dominica & American golden-plover & migrant \\ 
  Shorebirds  & Pluvialis squatarola & Black-bellied plover & migrant \\ 
  Shorebirds  & Charadrius hiaticula & Common Ringed plover & migrant \\ 
  Shorebirds  & Arenaria interpres & Ruddy turnstone & migrant \\ 
  Shorebirds  & Calidris canutus & Red knot & migrant \\ 
  Shorebirds  & Calidris melanotos & Pectoral sandpiper & migrant \\ 
  Shorebirds  & Calidris bairdii & Baird's sandpiper & migrant \\ 
  Shorebirds  & Calidris fuscicollis & White-rumped sandpiper & migrant \\ 
  Shorebirds  & Calidris subruficollis & Buff-breasted sandpiper & migrant \\ 
  Shorebirds  & Phalaropus fulicarius & Red phalarope & migrant \\ 
  Gulls  & Larus hyperboreus & Glaucous gull & migrant \\ 
  Jaegers  & Stercorarius longicaudus & Long-tailed jaeger & migrant \\ 
  Jaegers  & Stercorarius parasiticus & Parasitic jaeger & migrant \\ 
  Ravens  & Corvus corax & Common raven & partial migrant \\ 
  Passerines & Eremophila alpestris & Horned lark & migrant \\ 
  Passerines & Anthus rubescens & American pipit & migrant \\ 
  Passerines & Calcarius lapponicus & Lapland longspur & migrant \\ 
  Passerines & Plectrophenax nivalis & Snow bunting & migrant \\ 
  Lemmings  & Lemmus trimucronatus & Nearctic brown lemming & resident \\ 
  Lemmings  & Dicrostonyx groenlandicus & Nearctic collared lemming & resident \\ 
  Hares  & Lepus arcticus & Arctic hare & resident \\ 
  Ermines  & Mustela richardsonii & Ermine & resident \\ 
  Foxes  & Vulpes lagopus & Arctic fox & partial migrant \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Thu Oct  3 11:06:53 2024
\begin{table}[ht]
\centering
\caption{Species of the vertebrate community of Bylot Island and their corresponding migratory status (i.e., resident, partial migrant or migrant).} 
\label{table:table_species_name_strategy}
\begingroup\fontsize{10pt}{10pt}\selectfont
\begin{tabularx}{0.97\textwidth}{llll}
  \hline
{\textbf{Functional group}} & {\textbf{Scientific name}} & {\textbf{English name}} & {\textbf{Migratory status}} \\ 
  \hline
Ducks and loons  & {\emph{ Gavia pacifica}} & Pacific loon & migrant \\ 
  Ducks and loons  & {\emph{ Gavia stellata}} & Red-throated loon & migrant \\ 
  Ducks and loons  & {\emph{ Somateria spectabilis}} & King eider & migrant \\ 
  Ducks and loons  & {\emph{ Clangula hyemalis}} & Long-tailed duck & migrant \\ 
  Geese and swans  & {\emph{ Branta hutchinsii}} & Cackling goose & migrant \\ 
  Geese and swans  & {\emph{ Anser caerulescens}} & Snow goose & migrant \\ 
  Geese and swans  & {\emph{ Cygnus columbianus}} & Tundra swan & migrant \\ 
  Raptors  & {\emph{ Buteo lagopus}} & Rough-legged hawk & migrant \\ 
  Raptors  & {\emph{ Falco peregrinus}} & Peregrine falcon & migrant \\ 
  Raptors  & {\emph{ Bubo scandiacus}} & Snowy owl & migrant \\ 
  Ptarmigans  & {\emph{ Lagopus muta}} & Rock ptarmigan & resident \\ 
  Cranes  & {\emph{ Antigone canadensis}} & Sandhill crane & migrant \\ 
  Shorebirds  & {\emph{ Pluvialis dominica}} & American golden-plover & migrant \\ 
  Shorebirds  & {\emph{ Pluvialis squatarola}} & Black-bellied plover & migrant \\ 
  Shorebirds  & {\emph{ Charadrius hiaticula}} & Common-ringed plover & migrant \\ 
  Shorebirds  & {\emph{ Arenaria interpres}} & Ruddy turnstone & migrant \\ 
  Shorebirds  & {\emph{ Calidris canutus}} & Red knot & migrant \\ 
  Shorebirds  & {\emph{ Calidris melanotos}} & Pectoral sandpiper & migrant \\ 
  Shorebirds  & {\emph{ Calidris bairdii}} & Baird's sandpiper & migrant \\ 
  Shorebirds  & {\emph{ Calidris fuscicollis}} & White-rumped sandpiper & migrant \\ 
  Shorebirds  & {\emph{ Calidris subruficollis}} & Buff-breasted sandpiper & migrant \\ 
  Shorebirds  & {\emph{ Phalaropus fulicarius}} & Red phalarope & migrant \\ 
  Gulls  & {\emph{ Larus hyperboreus}} & Glaucous gull & migrant \\ 
  Jaegers  & {\emph{ Stercorarius longicaudus}} & Long-tailed jaeger & migrant \\ 
  Jaegers  & {\emph{ Stercorarius parasiticus}} & Parasitic jaeger & migrant \\ 
  Ravens  & {\emph{ Corvus corax}} & Common raven & partial migrant \\ 
  Passerines & {\emph{ Eremophila alpestris}} & Horned lark & migrant \\ 
  Passerines & {\emph{ Anthus rubescens}} & American pipit & migrant \\ 
  Passerines & {\emph{ Calcarius lapponicus}} & Lapland longspur & migrant \\ 
  Passerines & {\emph{ Plectrophenax nivalis}} & Snow bunting & migrant \\ 
  Lemmings  & {\emph{ Lemmus trimucronatus}} & Nearctic brown lemming & resident \\ 
  Lemmings  & {\emph{ Dicrostonyx groenlandicus}} & Nearctic collared lemming & resident \\ 
  Hares  & {\emph{ Lepus arcticus}} & Arctic hare & resident \\ 
  Ermines  & {\emph{ Mustela richardsonii}} & Ermine & resident \\ 
  Foxes  & {\emph{ Vulpes lagopus}} & Arctic fox & partial migrant \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}

### 2024-10-03 MetadataS1/tables/table_species_year_monitoring.tex
Revision of the entire document and minor changes

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Tue Oct  1 09:17:34 2024
\begin{table}[ht]
\centering
\caption{Summary of vertebrate species monitoring in the Bylot Island study area. In this paper, we excluded certain years for specific species due to reduced sampling efforts. As a result, duration of times series presented here may differ slightly from those in Gauthier et al. (2024b).} 
\label{table:table_species_year_monitoring}
\begingroup\fontsize{8pt}{10pt}\selectfont
\begin{tabularx}{\textwidth}{lllll}
  \hline
Species & Zone & Years & Number of years & Monitoring \\ 
  \hline
Snow goose & camp 2 & 1999-2019, 2023 & (22) & systematic \\ 
  Rough-legged hawk & qarlikt., black \& south plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Peregrine falcon & qarlikt., black \& south plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Snowy owl & qarlikt., black \& south plat. & 1996-2019, 2023 & (25) & systematic \\ 
  Baird's sandpiper & qarlikturvik (2x1 km plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Lapland longspur & qarlikturvik (2x1 km plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  King eider & qarlikturvik (4x2 km plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Long-tailed duck & qarlikturvik (4x2 km plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Rock ptarmigan & qarlikturvik (4x2 km plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Sandhill crane & qarlikturvik (4x2 km plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Nearctic brown lemming & qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Nearctic collared lemming & qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Pacific loon & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Red-throated loon & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Cackling goose & qarlikturvik valley & 2004-2019, 2022-2023 & (18) & systematic \\ 
  Tundra swan & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Glaucous gull & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Long-tailed jaeger & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Pacific loon & whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Red-throated loon & whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Cackling goose & whole study area & 2017-2019, 2022-2023 & (5) & systematic \\ 
  Tundra swan & whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Rough-legged hawk & whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Peregrine falcon & whole study area & 2013-2019, 2022  & (8) & systematic \\ 
  Snowy owl & whole study area & 2012-2019, 2022-2023 & (10) & systematic \\ 
  Common Ringed plover & whole study area & 2015-2017 & (3) & systematic \\ 
  Glaucous gull & whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Parasitic jaeger & whole study area & 2009-2019, 2022 & (12) & opportunistic \\ 
  Common raven & whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Ermine & whole study area & 1993-2019 & (27) & opportunistic \\ 
  Arctic fox & whole study area & 2008-2016 & (9) & systematic \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Thu Oct  3 13:54:34 2024
\begin{table}[ht]
\centering
\caption{Summary of vertebrate species monitoring in the Bylot Island study area. In this paper, we excluded certain years for specific species due to reduced sampling efforts. As a result, duration of times series presented here may differ slightly from those in Gauthier et al. (2024b).} 
\label{table:table_species_year_monitoring}
\begingroup\fontsize{8pt}{10pt}\selectfont
\begin{tabularx}{\textwidth}{lllll}
  \hline
{\textbf{Species}} & {\textbf{Zone}} & {\textbf{Years}} & {\textbf{Number of years}} & {\textbf{Monitoring}} \\ 
  \hline
Pacific loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Pacific loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Red-throated loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Red-throated loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  King eider & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Long-tailed duck & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Cackling goose & Qarlikturvik valley & 2004-2019, 2022-2023 & (18) & systematic \\ 
  Cackling goose & Whole study area & 2017-2019, 2022-2023 & (5) & systematic \\ 
  Snow goose & Camp 2 & 1999-2019, 2023 & (22) & systematic \\ 
  Tundra swan & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Tundra swan & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Rough-legged hawk & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Rough-legged hawk & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Peregrine falcon & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Peregrine falcon & Whole study area & 2013-2019, 2022  & (8) & systematic \\ 
  Snowy owl & Qarlikt., Black \& South plat. & 1996-2019, 2023 & (25) & systematic \\ 
  Snowy owl & Whole study area & 2012-2019, 2022-2023 & (10) & systematic \\ 
  Rock ptarmigan & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Sandhill crane & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Common-ringed plover & Whole study area & 2015-2017 & (3) & systematic \\ 
  Baird's sandpiper & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Glaucous gull & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Glaucous gull & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Long-tailed jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & Whole study area & 2009-2019, 2022 & (12) & opportunistic \\ 
  Common raven & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Lapland longspur & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Nearctic brown lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Nearctic collared lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Ermine & Whole study area & 1993-2019 & (27) & opportunistic \\ 
  Arctic fox & Whole study area & 2008-2016 & (9) & systematic \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}
